Market simulator

### 2020-09-24 analysis/05_market_simulator.Rmd

# Assign covariate labels
per_table$levels <- c(
  # Intercept
  "Intercept",
  # Follow national news
  "Once a week",
  "At least once a day",
  # Follow international news
  "Sometimes",
  "Always",
  # Mediums to follow news
  "TV",
  "Print",
  "Online (not social media)",
  "Social media",
  "Radio",
  "Email newsletter",
  "News app",
  # Follow government and public affairs
  "Often", 
  # Traveled to a developing country
  "Traveled to a developing country", 
  # Liberal to Conservative
  "Somewhat liberal",
  "Slightly liberal",
  "Moderate",
  "Slightly conservative",
  "Somewhat conservative",
  "Extremely conservative",
  # Trust in political institutions
  "Very little trust in political institutions",
  "Little trust in political institutions",
  "Neutral trust in political institutions",
  "Some trust in political institutions",
  "A lot of trust in political institutions",
  "Complete trust in political institutions",
  # People should be more charitable
  "Disagree",
  "Somewhat disagree",
  "Neutral",
  "Somewhat agree",
  "Agree",
  "Strongly agree",
  # Religious attendance
  "Rarely attend",
  "Attend at least once a month",
  # Importance of religion
  "Important",
  # Religion
  "Protestant",
  "Christian Orthodox",
  "Jewish",
  "Muslim",
  "Sikh",
  "Hindu",
  "Buddhist",
  "Atheist",
  "Other religion",
  # Importance of trusing charities
  "Very unimportant",
  "Somewhat unimportant",
  "Neutral",
  "Somewhat important",
  "Very important",
  "Essential",
  # Trust in charities
  "Very little trust in charities",
  "Little trust in charities",
  "Neutral trust in charities",
  "Some trust in charities",
  "A lot of trust in charities",
  "Complete trust in charities",
  # Donation frequency
  "Donate at least once a month", 
  # Donated last year
  "$50-$99",
  "$100-$499",
  "$500-$999",
  "$1,000-$4,999",
  "$5,000-$9,999",
  "$10,000 +",
  # Volunteered in past 12 months
  "Volunteered in past 12 months",
  # Volunteer frequency
  "Rarely volunteer",
  "Volunteer more than once a month, less than once a year",
  "Volunteer at least once a month",
  # History of activism
  "Personally involved",
  # History of family activism
  "Family involved",
  # Church or religious organization
  "Inactive church member",
  "Active church member",
  # Sport or recreational organization
  "Inactive sports or rec organization member",
  "Active sports or rec organization member", 
  # Art, music, or educational organization
  "Inactive art, music, or educational organization member",
  "Active art, music, or educational organization member",
  # Labor union
  "Inactive union member",
  "Active union member",
  # Political party
  "Inactive political party member",
  "Active political party member",
  # Environmental organization
  "Inactive environmental organization member",
  "Active environmental organization member",
  # Professional association
  "Inactive professional association member",
  "Active professional association member",
  # Humanitarian or charitable organization
  "Inactive humanitarian or charitable organization member",
  "Active humanitarian or charitable organization member",
  # Consumer organization
  "Inactive consumer organization member",
  "Active consumer organization member",
  # Other organization
  "Inactive member in another organization",
  "Active member in another organization",
  # Gender
  "Female",
  "Transgender",
  "Prefer not to say",
  "Other gender",
  # Marital status
  "Widowed",
  "Divorced",
  "Separated",
  "Never married",
  # Education
  "High school graduate", 
  "Some college",
  "2 year degree",
  "4 year degree",
  "Graduate or professional degree",
  "Doctorate",
  # Income
  "More than median of $61,372", 
  # Race
  "White", 
  "Black or African American", 
  "American Indian or Alaskan Native", 
  "Asian", 
  "Native Hawaiian or Pacific Islander",
  "Other race",
  # Age
  "More than median age of 36"
)

@@

  ggplotly(
    plot_data %>% 
      # Factor Organization and Persona with ordered=TRUE
      mutate(
        Organization = factor(
          Organization, 
          levels = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name), 
          ordered = TRUE
        ),
        Persona = factor(
          Persona, 
          levels = c(input$per1_name, input$per2_name, input$per3_name), 
          ordered = TRUE
        )
      ) %>% 
      ggplot(aes(y = Value, x = Organization, fill = Persona)) +
      geom_bar(position = "dodge", stat = "identity") +
      labs(x="", y = "Market Share") + 
      scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
      theme(
        legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major.y = element_line(color = "#D3D3D3")
      )
    )
})
```

@@

# People should be more charitable
selectInput(
  "per1_others_charitable",
  label = "People should be more charitable:",
  choices = c(
    "Strongly Disagree",
    "Disagree",
    "Somewhat disagree",
    "Neutral",
    "Somewhat agree",
    "Agree",
    "Strongly agree"
  ),
  selected = "Strongly agree",
  width = "450px"
)

@@

# Importance of trusting charities
selectInput(
  "per1_charity_importance",
  label = "Charity Importance:",
  choices = c(
    "Not at all important",
    "Very unimportant",
    "Somewhat unimportant",
    "Neutral",
    "Somewhat important",
    "Very important",
    "Essential"
  ),
  selected = "Somewhat unimportant",
  width = "450px"
)

@@

# Donated last year
selectInput(
  "per1_donation_amount",
  label = "Donation Amount:",
  choices = c(
    '$1-$49',
    '$50-$99',
    '$100-$499',
    '$500-$999',
    '$1,000-$4,999',
    '$5,000-$9,999',
    '$10,000+'
  ),
  selected = "$100-$499",
  width = "450px"
)

@@

# People should be more charitable
selectInput(
  "per2_others_charitable",
  label = "People should be more charitable:",
  choices = c(
    "Strongly Disagree",
    "Disagree",
    "Somewhat disagree",
    "Neutral",
    "Somewhat agree",
    "Agree",
    "Strongly agree"
  ),
  selected = "Strongly agree",
  width = "450px"
)

@@

# Importance of trusting charities
selectInput(
  "per2_charity_importance",
  label = "Charity Importance:",
  choices = c(
    "Not at all important",
    "Very unimportant",
    "Somewhat unimportant",
    "Neutral",
    "Somewhat important",
    "Very important",
    "Essential"
  ),
  selected = "Somewhat unimportant",
  width = "450px"
)

@@

# Donated last year
selectInput(
  "per2_donation_amount",
  label = "Donation Amount:",
  choices = c(
    '$1-$49',
    '$50-$99',
    '$100-$499',
    '$500-$999',
    '$1,000-$4,999',
    '$5,000-$9,999',
    '$10,000+'
  ),
  selected = "$100-$499",
  width = "450px"
)

@@

# People should be more charitable
selectInput(
  "per3_others_charitable",
  label = "People should be more charitable:",
  choices = c(
    "Strongly Disagree",
    "Disagree",
    "Somewhat disagree",
    "Neutral",
    "Somewhat agree",
    "Agree",
    "Strongly agree"
  ),
  selected = "Strongly agree",
  width = "450px"
)

@@

# Importance of trusting charities
selectInput(
  "per3_charity_importance",
  label = "Charity Importance:",
  choices = c(
    "Not at all important",
    "Very unimportant",
    "Somewhat unimportant",
    "Neutral",
    "Somewhat important",
    "Very important",
    "Essential"
  ),
  selected = "Somewhat unimportant",
  width = "450px"
)

@@

# Donated last year
selectInput(
  "per3_donation_amount",
  label = "Donation Amount:",
  choices = c(
    '$1-$49',
    '$50-$99',
    '$100-$499',
    '$500-$999',
    '$1,000-$4,999',
    '$5,000-$9,999',
    '$10,000+'
  ),
  selected = "$100-$499",
  width = "450px"
)

>>>>

# Assign covariate labels
per_table$levels <- c(
  # Intercept
  "Intercept",
  # Follow national news
  "Once a week",
  "At least once a day",
  # Follow international news
  "Sometimes",
  "Always",
  # Mediums to follow news
  "TV",
  "Print",
  "Online (not social media)",
  "Social media",
  "Radio",
  "Email newsletter",
  "News app",
  # Follow government and public affairs
  "Often", 
  # Traveled to a developing country
  "Traveled to a developing country", 
  # Liberal to Conservative
  "Somewhat liberal",
  "Slightly liberal",
  "Moderate",
  "Slightly conservative",
  "Somewhat conservative",
  "Extremely conservative",
  # Trust in political institutions
  "Very little trust in political institutions",
  "Little trust in political institutions",
  "Neutral trust in political institutions",
  "Some trust in political institutions",
  "A lot of trust in political institutions",
  "Complete trust in political institutions",
  # People should be more charitable
  "Disagree",
  "Somewhat disagree",
  "Neutral",
  "Somewhat agree",
  "Agree",
  "Strongly agree",
  # Religious attendance
  "Rarely attend",
  "Attend at least once a month",
  # Importance of religion
  "Important",
  # Religion
  "Protestant",
  "Christian Orthodox",
  "Jewish",
  "Muslim",
  "Sikh",
  "Hindu",
  "Buddhist",
  "Atheist",
  "Other religion",
  # Importance of trusting charities
  "Very unimportant",
  "Somewhat unimportant",
  "Neutral importance",
  "Somewhat important",
  "Very important",
  "Essential",
  # Trust in charities
  "Very little trust in charities",
  "Little trust in charities",
  "Neutral trust in charities",
  "Some trust in charities",
  "A lot of trust in charities",
  "Complete trust in charities",
  # Donation frequency
  "Donate at least once a month", 
  # Donated last year
  "$50-$99",
  "$100-$499",
  "$500-$999",
  "$1,000-$4,999",
  "$5,000-$9,999",
  "$10,000+",
  # Volunteered in past 12 months
  "Volunteered in past 12 months",
  # Volunteer frequency
  "Rarely volunteer",
  "Volunteer more than once a month, less than once a year",
  "Volunteer at least once a month",
  # History of activism
  "Personally involved",
  # History of family activism
  "Family involved",
  # Church or religious organization
  "Inactive church member",
  "Active church member",
  # Sport or recreational organization
  "Inactive sports or rec organization member",
  "Active sports or rec organization member", 
  # Art, music, or educational organization
  "Inactive art, music, or educational organization member",
  "Active art, music, or educational organization member",
  # Labor union
  "Inactive union member",
  "Active union member",
  # Political party
  "Inactive political party member",
  "Active political party member",
  # Environmental organization
  "Inactive environmental organization member",
  "Active environmental organization member",
  # Professional association
  "Inactive professional association member",
  "Active professional association member",
  # Humanitarian or charitable organization
  "Inactive humanitarian or charitable organization member",
  "Active humanitarian or charitable organization member",
  # Consumer organization
  "Inactive consumer organization member",
  "Active consumer organization member",
  # Other organization
  "Inactive member in another organization",
  "Active member in another organization",
  # Gender
  "Female",
  "Transgender",
  "Prefer not to say",
  "Other gender",
  # Marital status
  "Widowed",
  "Divorced",
  "Separated",
  "Never married",
  # Education
  "High school graduate", 
  "Some college",
  "2 year degree",
  "4 year degree",
  "Graduate or professional degree",
  "Doctorate",
  # Income
  "More than median of $61,372", 
  # Race
  "White", 
  "Black or African American", 
  "American Indian or Alaskan Native", 
  "Asian", 
  "Native Hawaiian or Pacific Islander",
  "Other race",
  # Age
  "More than median age of 36"
)

@@

  ggplotly(
    plot_data %>% 
      # Factor Organization and Persona with ordered=TRUE
      mutate(
        Organization = factor(
          Organization, 
          levels = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name), 
          ordered = TRUE
        ),
        Persona = factor(
          Persona, 
          levels = c(input$per1_name, input$per2_name, input$per3_name), 
          ordered = TRUE
        )
      ) %>% 
      ggplot(aes(y = Value, x = Organization, fill = Persona)) +
      geom_bar(position = "dodge", stat = "identity") +
      labs(x="", y = "Market Share") + 
      scale_fill_manual(values = c("#FFC30B", "#28a153", "#c23838")) +
      theme(
        legend.position = "right",
        panel.background = element_blank(),
        panel.grid.major.y = element_line(color = "#D3D3D3")
      )
    )
})

# Compute and render the market share as a table
renderTable({
  org_choice = org_reactive()
  per_choice = per_reactive()

  # Table
  data <- data.frame(
    Shares = c(
      # Persona 1
      per1_org1_share, per1_org2_share, per1_org3_share, per1_org4_share, 
      # Persona 2
      per2_org1_share, per2_org2_share, per2_org3_share, per2_org4_share,
      # Persona 3
      per3_org1_share, per3_org2_share, per3_org3_share, per3_org4_share
    ),
    Organization = c(input$org1_name, input$org2_name, input$org3_name, input$org4_name),
    Persona = c(
      rep(input$per1_name, 4), 
      rep(input$per2_name, 4), 
      rep(input$per3_name, 4)
    )
  ) %>% 
    pivot_wider(names_from = Persona, values_from = Shares)

  data
})
```

@@

# People should be more charitable
selectInput(
  "per1_others_charitable",
  label = "People should be more charitable:",
  choices = c(
    "Strongly disagree",
    "Disagree",
    "Somewhat disagree",
    "Neutral",
    "Somewhat agree",
    "Agree",
    "Strongly agree"
  ),
  selected = "Strongly agree",
  width = "450px"
)

@@

# Importance of trusting charities
selectInput(
  "per1_charity_importance",
  label = "Charity Importance:",
  choices = c(
    "Not at all important",
    "Very unimportant",
    "Somewhat unimportant",
    "Neutral importance",
    "Somewhat important",
    "Very important",
    "Essential"
  ),
  selected = "Somewhat unimportant",
  width = "450px"
)

@@

# Donated last year
selectInput(
  "per1_donation_amount",
  label = "Donation Amount Last Year:",
  choices = c(
    '$1-$49',
    '$50-$99',
    '$100-$499',
    '$500-$999',
    '$1,000-$4,999',
    '$5,000-$9,999',
    '$10,000+'
  ),
  selected = "$100-$499",
  width = "450px"
)

@@

# People should be more charitable
selectInput(
  "per2_others_charitable",
  label = "People should be more charitable:",
  choices = c(
    "Strongly disagree",
    "Disagree",
    "Somewhat disagree",
    "Neutral",
    "Somewhat agree",
    "Agree",
    "Strongly agree"
  ),
  selected = "Strongly agree",
  width = "450px"
)

@@

# Importance of trusting charities
selectInput(
  "per2_charity_importance",
  label = "Charity Importance:",
  choices = c(
    "Not at all important",
    "Very unimportant",
    "Somewhat unimportant",
    "Neutral importance",
    "Somewhat important",
    "Very important",
    "Essential"
  ),
  selected = "Somewhat unimportant",
  width = "450px"
)

@@

# Donated last year
selectInput(
  "per2_donation_amount",
  label = "Donation Amount Last Year:",
  choices = c(
    '$1-$49',
    '$50-$99',
    '$100-$499',
    '$500-$999',
    '$1,000-$4,999',
    '$5,000-$9,999',
    '$10,000+'
  ),
  selected = "$100-$499",
  width = "450px"
)

@@

# People should be more charitable
selectInput(
  "per3_others_charitable",
  label = "People should be more charitable:",
  choices = c(
    "Strongly disagree",
    "Disagree",
    "Somewhat disagree",
    "Neutral",
    "Somewhat agree",
    "Agree",
    "Strongly agree"
  ),
  selected = "Strongly agree",
  width = "450px"
)

@@

# Importance of trusting charities
selectInput(
  "per3_charity_importance",
  label = "Charity Importance:",
  choices = c(
    "Not at all important",
    "Very unimportant",
    "Somewhat unimportant",
    "Neutral importance",
    "Somewhat important",
    "Very important",
    "Essential"
  ),
  selected = "Somewhat unimportant",
  width = "450px"
)

@@

# Donated last year
selectInput(
  "per3_donation_amount",
  label = "Donation Amount Last Year:",
  choices = c(
    '$1-$49',
    '$50-$99',
    '$100-$499',
    '$500-$999',
    '$1,000-$4,999',
    '$5,000-$9,999',
    '$10,000+'
  ),
  selected = "$100-$499",
  width = "450px"
)
